Thesis Title

### 2023-01-23 chapters/introduction.tex
Add sections to thesis body

In public health microbiology, \ac{SMg} combined with transmission network analysis allowed the investigation and quick action on the food supply of the 2013 outbreak of \ac{STEC} strain O104:H4 from faecal specimens obtained from patients \citep{loman_culture-independent_2013}. A similar approach was followed in the detection of \textit{Salmonella enterica} subsp. \textit{enterica} serovar Heidelberg from faecal samples in two though to be unrelated outbreaks in the United States of America, as well as the \textit{in situ} abundance and level of intrapopulation diversity of the pathogen, and the possibility of co-infections with \textit{Staphylococcus aureus}, overgrowth of commensal \textit{Escherichia coli}, and significant shifts in the gut microbiome during infection relative to reference healthy samples \citep{huang_metagenomics_2017}. More recently, shotgun metagenomic sequencing has evidenced alterations in the gut microbiota of a subset of COVID-19 patients that present the uncommon gastrointestinal (GI) symptoms, shedding a higher understanding of gut–lung axis affecting the progression of COVID-19 \citep{li_microbiome_2021}.

>>>>

In public health microbiology, \ac{SMg} combined with transmission network analysis allowed the investigation and quick action on the food supply of the 2013 outbreak of \ac{STEC} strain O104:H4 from faecal specimens obtained from patients \citep{loman_culture-independent_2013}. A similar approach was followed in the detection of \textit{Salmonella enterica} subsp. \textit{enterica} serovar Heidelberg from faecal samples in two thought to be unrelated outbreaks in the United States of America, as well as the \textit{in situ} abundance and level of intrapopulation diversity of the pathogen, and the possibility of co-infections with \textit{Staphylococcus aureus}, overgrowth of commensal \textit{Escherichia coli}, and significant shifts in the gut microbiome during infection relative to reference healthy samples \citep{huang_metagenomics_2017}. More recently, shotgun metagenomic sequencing has evidenced alterations in the gut microbiota of a subset of COVID-19 patients that present the uncommon gastrointestinal (GI) symptoms, shedding a higher understanding of gut–lung axis affecting the progression of COVID-19 \citep{li_microbiome_2021}.

### 2023-01-23 main.tex
start discussion
Updates from Overleaf
Revert "start discussion"
This reverts commit edfc8947b90b00c7968d6707c7048c0254029344.
update with working version
start conclusion
Add abstract - first draft; Minor copyediting
fix bug
add hAMRonization paper
Add sections to thesis body

%-----------------------------------------------------------------
% Acknowledgements
%------------------------------------------------------------------
\newpage
\thispagestyle{plain}
\addcontentsline{toc}{chapter}{Acknowledgements}
\chapter*{Acknowledgements}
\clearpage \thispagestyle{empty}\mbox{}\clearpage

%-----------------------------------------------------------------
% Summary
%------------------------------------------------------------------
\newpage
\thispagestyle{plain}
\addcontentsline{toc}{chapter}{Summary}
\chapter*{Summary}

\keywords{one, two, three, four, five}
\clearpage \thispagestyle{empty}\mbox{}\clearpage

%-----------------------------------------------------------------
% Resumo
%------------------------------------------------------------------
\newpage
\thispagestyle{plain}
\addcontentsline{toc}{chapter}{Resumo}
\chapter*{Resumo}

\keywords{um, dois, três, quatro, cinco}
\clearpage \thispagestyle{empty}\mbox{}\clearpage

%-----------------------------------------------------------------
% Thesis Outline
%------------------------------------------------------------------
\newpage
\thispagestyle{plain}
\addcontentsline{toc}{chapter}{Thesis Outline}
\chapter*{Thesis Outline}
%\input{chapters/thesis_outline}
\clearpage \thispagestyle{empty}\mbox{}\clearpage

%-----------------------------------------------------------------
% Abbreviations
%------------------------------------------------------------------
\newpage
\thispagestyle{plain}
\addcontentsline{toc}{chapter}{Abbreviation}
\chapter*{Abbreviation}
I \input{chapters/acconyms}
\clearpage \thispagestyle{empty}\mbox{}\clearpage

@@

%-----------------------------------------------------------------
% Introduction
%------------------------------------------------------------------
\newpage
\thispagestyle{empty}
\chapter{General Introduction\label{ch:introduction}}
\thispagestyle{empty}
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\begin{refsection}
%\include{chapters/introduction}
\newpage
\section{References}
\printbibliography[heading=none]
\end{refsection}

%-----------------------------------------------------------------
% Paper 1 - Natacha
%------------------------------------------------------------------
\newpage
\thispagestyle{empty}
\chapter{Critical steps in clinical shotgun metagenomics for the concomitant detection and typing of microbial pathogens\label{ch:paper1}}

\thispagestyle{empty}
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\begin{refsection}
%\include{chapters/chapter_2}
\newpage
\section{References}
\printbibliography[heading=none]
\end{refsection}

@@

\thispagestyle{empty}
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\begin{refsection}
%\include{chapters/chapter_3}
\newpage
\section{References}
\printbibliography[heading=none]
\end{refsection}

@@

\thispagestyle{empty}
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\begin{refsection}
%\include{chapters/chapter_4}
\newpage
\section{References}
\printbibliography[heading=none]
\end{refsection}

%-----------------------------------------------------------------
% Paper 4 - LMAS
%------------------------------------------------------------------
\newpage
\thispagestyle{empty}
\chapter{LMAS: Last Metagenomic Assembler Standing\label{ch:paper4}}

\thispagestyle{empty}
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\begin{refsection}
%\include{chapters/chapter_5}
\newpage
\section{References}
\printbibliography[heading=none]
\end{refsection}

%-----------------------------------------------------------------
% Paper 5 - hAMRonization
%------------------------------------------------------------------
\newpage
\thispagestyle{empty}
\chapter{hAMRonization: Enhancing antimicrobial resistance prediction using PHA4GE standards and specification\label{ch:paper5}}

\thispagestyle{empty}
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\begin{refsection}
%\include{chapters/chapter_6}
\newpage
\section{References}
\printbibliography[heading=none]
\end{refsection}

@@

%-----------------------------------------------------------------
% Conclusion
%-----------------------------------------------------------------
\newpage
\chapter{Conclusion \label{ch:conclusion}}
\thispagestyle{empty}
\newpage
\include{chapters/conclusion}

%-----------------------------------------------------------------
% Appendix
%-----------------------------------------------------------------
\appendix
\chapter{Appendix}
\include{chapters/appendix}
%\includepdf[pages={1-}]{resources/papers/s41598-018-31873-w.pdf}
%\includepdf[pages={1-}]{resources/papers/dkz363.pdf}
%\includepdf[pages={1-}]{resources/papers/mgen000328.pdf}

>>>>

%-----------------------------------------------------------------
% Acknowledgements
%------------------------------------------------------------------
\newpage
\thispagestyle{plain}
\addcontentsline{toc}{chapter}{Acknowledgements}
\chapter*{Acknowledgements}
\input{chapters/acknowledgements.tex}
\clearpage \thispagestyle{empty}\mbox{}\clearpage

%-----------------------------------------------------------------
% Summary
%------------------------------------------------------------------
\newpage
\thispagestyle{plain}
\addcontentsline{toc}{chapter}{Summary}
\chapter*{Summary}
\input{chapters/abstract.tex}

\keywords{Clinical Microbiology, Genome Sequencing, Metagenomics, Reproducibility, Interoperability}
\clearpage \thispagestyle{empty}\mbox{}\clearpage

%-----------------------------------------------------------------
% Resumo
%------------------------------------------------------------------
\newpage
\thispagestyle{plain}
\addcontentsline{toc}{chapter}{Resumo}
\chapter*{Resumo}
\input{chapters/resumo.tex}

\keywords{Microbiologia Clínica, Sequênciação genómica, Metagenómica, Reproducibilidade, Interoperabilidade}
\clearpage \thispagestyle{empty}\mbox{}\clearpage

%-----------------------------------------------------------------
% Thesis Outline
%------------------------------------------------------------------
\newpage
\thispagestyle{plain}
\addcontentsline{toc}{chapter}{Thesis Outline}
\chapter*{Thesis Outline}
\input{chapters/thesis_outline}
\clearpage \thispagestyle{empty}\mbox{}\clearpage

%-----------------------------------------------------------------
% Abbreviations
%------------------------------------------------------------------
\newpage
\thispagestyle{plain}
\addcontentsline{toc}{chapter}{Abbreviation}
\chapter*{Abbreviation}
\input{chapters/acconyms}
\clearpage \thispagestyle{empty}\mbox{}\clearpage

@@

%-----------------------------------------------------------------
% Introduction
%------------------------------------------------------------------
\newpage
\thispagestyle{empty}
\chapter{General Introduction\label{ch:introduction}}
\thispagestyle{empty}
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\begin{refsection}
\include{chapters/introduction}
\newpage
\section{References}
\printbibliography[heading=none]
\end{refsection}

\part{Applying metagenomics in the clinical context}
%-----------------------------------------------------------------
% Paper 1 - Natacha
%------------------------------------------------------------------
\newpage
\thispagestyle{empty}
\chapter{Critical steps in clinical shotgun metagenomics for the concomitant detection and typing of microbial pathogens\label{ch:paper1}}

\thispagestyle{empty}
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\begin{refsection}
\include{chapters/chapter_2}
\newpage
\section{References}
\printbibliography[heading=none]
\end{refsection}

@@

\thispagestyle{empty}
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\begin{refsection}
\include{chapters/chapter_3}
\newpage
\section{References}
\printbibliography[heading=none]
\end{refsection}

@@

\thispagestyle{empty}
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\begin{refsection}
\include{chapters/chapter_4}
\newpage
\section{References}
\printbibliography[heading=none]
\end{refsection}

\part{Impact of \textit{de novo} assemblers in metagenomics}
%-----------------------------------------------------------------
% Paper 4 - LMAS
%------------------------------------------------------------------
\newpage
\thispagestyle{empty}
\chapter{LMAS: Last Metagenomic Assembler Standing\label{ch:paper4}}

\thispagestyle{empty}
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\begin{refsection}
\include{chapters/chapter_5}
\newpage
\section{References}
\printbibliography[heading=none]
\end{refsection}

\part{Challenges of data availability in metagenomics and beyond}
%-----------------------------------------------------------------
% Paper 5 - hAMRonization
%------------------------------------------------------------------
\newpage
\thispagestyle{empty}
\chapter{hAMRonization: Enhancing antimicrobial resistance prediction using PHA4GE standards and specification\label{ch:paper5}}

\thispagestyle{empty}
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\begin{refsection}
\include{chapters/chapter_6}
\newpage
\section{References}
\printbibliography[heading=none]
\end{refsection}

@@

\part{Crowdsourcing for software robustness in metagenomics and beyond}
%-----------------------------------------------------------------
% Paper 7 - Software Testing
%------------------------------------------------------------------
\newpage
\thispagestyle{empty}
\chapter{Software testing in microbial bioinformatics: a call to action\label{ch:paper7}}

\thispagestyle{empty}
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\begin{refsection}
\include{chapters/chapter_8}
\newpage
\section{References}
\printbibliography[heading=none]
\end{refsection}

%-----------------------------------------------------------------
% Discussion
%-----------------------------------------------------------------

\newpage
\thispagestyle{empty}
\chapter{General Discussion \label{ch:discussion}}

\clearpage \thispagestyle{empty}\mbox{}\clearpage
\begin{refsection}
\include{chapters/discussion}
\newpage
\section{References}
\printbibliography[heading=none]
\end{refsection}

%-----------------------------------------------------------------
% Conclusion
%-----------------------------------------------------------------
\newpage
\chapter{Conclusion \label{ch:conclusion}}

\clearpage \thispagestyle{empty}\mbox{}\clearpage
\begin{conclusion}
\include{chapters/conclusion}
\newpage
\section{References}
\printbibliography[heading=none]
\end{conclusion}

%-----------------------------------------------------------------
% Appendix
%-----------------------------------------------------------------
%\appendix
\newpage
\chapter{Appendix}
\includepdf[pages={1-}]{resources/papers/s41598-018-31873-w.pdf}
\includepdf[pages={1-}]{resources/papers/dkz363.pdf}
\includepdf[pages={1-}]{resources/papers/mgen000328.pdf}
\includepdf[pages={1-}]{resources/papers/giac122.pdf}
\includepdf[pages={1-}]{resources/papers/giac003.pdf}
\includepdf[pages={1-}]{resources/papers/mgen000790.pdf}
